\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-11 doc/paper.tex
Related work

	\section{Related Work} \label{related-work} Visualizations excel for their
	ability to communicate information quickly and
	efficiently~\cite{baeza1999modern}; the visualization of spreadsheets,
	therefore, has offered much room for research. Several previous tools work
	within a spreadsheet, seeking to clarify the connections between the visible
	values in cells, the formulae that produce them, and the dependencies between
	cells that inform them. Igarashi and colleague's fluid
	visualizations~\cite{igarashi1998fluid}, for example, do this by imposing
	lines, color, and animation over the spreadsheet to visually explain these
	tangled connections. Likewise, Clermont explored ways of grouping cells by
	color and border that were related through similar functions, neighbors, or
	references~\cite{clermont2003scalable}, and Hipfl extended this work by
	incorporating the layouts and labels of spreadsheets~\cite{hipfl2008using}.
	Other tools focus on creating visualizations external to the sheets. Hermans
	and colleagues address a spreadsheet programmer's information needs by making
	dataflow diagrams from individual sheets through the tools
	GyroSAT~\cite{hermans2011supporting} and Breviz~\cite{hermans2011breviz}.
	\toolname is among the latter class, creating standalone visualizations about
	spreadsheets instead of drawing connections inside the spreadsheet itself. In
	contrast to the other visualization work, our work focuses on representing
	functions and how they combine into complex formulae, rather than exploring the
	data structures of any particular spreadsheet.  \par

	Many other tools inspect the structure of formulae but often from the
	perspective of finding bad design.  Following Fowler's initial description of
	code smells in object-oriented design~\cite{fowler2009refactoring}, many
	researchers have applied similar observations to spreadsheets and have
	cataloged classes of problematic
	formulae~\cite{hermans2012detecting}~\cite{cunha2012towards}~\cite{asavametha2012detecting}, often accompanying them with detection tools~\cite{abreu2014smelling} and investigations into real datasets~\cite{jansen2015code}. For example, Hermans, leveraging her work with the aforementioned dataflow diagrams, has worked with assessing common inter-worksheet smells, such as feature envy and inappropriate intimacy, wherein references between worksheets (rather than cells) in a file suggest a problem~\cite{hermans2012detectinginter}. Other tools, like Badame's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them. However, these studies define standards of poor design and orient their searches around them. Though \toolname supports the search for bad design, as we will see, the tool itself takes a much more agnostic approach in presentation, offering examples without regard for design quality. \par

	Implicit in this study is an exploration of the Excel API and how people use
	it. Previous research, such as the first study on the Enron
	spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS
	corpus~\cite{jansen2015enron}, quantifies how often users employ certain
	functions but not how they combine them. Researchers have applied such
	questions to other contexts as well, such as Murphy and colleague's study into
	how Java developers use Eclipse and what commands they use most
	often~\cite{murphy2006java}. Others focus on the documentation of the API
	itself: Robillard and DeLine, for example conducted a series of surveys and
	interviews to diagnose common problems with learning APIs, and they found that
	code examples, one of the focuses of this tool, is one of the most important
	aids to have in learning a new system~\cite{robillard2011field}. Though this
	paper applies the tool to the Enron corpus specifically, the tool itself is not
	limited to this; it can be readily applied to any collection of Excel
	spreadsheets a user gives it.

>>>>

	\section{Related Work} \label{related-work} Visualizations excel for their
	ability to communicate information quickly and
	efficiently~\cite{baeza1999modern}; the visualization of spreadsheets,
	therefore, offers much room for research. Several previous tools work
	within a spreadsheet, clarifying connections between the visible
	values in cells, the formulae that produce them, and the dependencies between
	cells that inform them. Igarashi and colleague's fluid
	visualizations~\cite{igarashi1998fluid}, for example, do this by imposing
	lines, color, and animation over the spreadsheet to visually explain these
	tangled connections. Likewise, Clermont explored ways of grouping cells by
	color and border that were related through similar functions, neighbors, or
	references~\cite{clermont2003scalable}, and Hipfl extended this work by
	incorporating the layouts and labels of spreadsheets~\cite{hipfl2008using}.

	Other tools focus on creating visualizations external to the sheets. Hermans
	and colleagues address a spreadsheet programmer's information needs by making
	dataflow diagrams from individual sheets through the tools
	GyroSAT~\cite{hermans2011supporting} and Breviz~\cite{hermans2011breviz}.
	\toolname is among this type, creating standalone visualizations about
	spreadsheets instead of drawing connections inside the spreadsheet itself. In
	contrast to the other visualization work, our work focuses on representing
	functions and how they combine into complex formulae, rather than exploring the
	data structures of any particular spreadsheet.  \par

	Many other tools inspect the structure of formulae but from the
	perspective of finding bad design.  Following Fowler's initial description of
	code smells in object-oriented design~\cite{fowler2009refactoring}, many
	researchers have applied similar observations to spreadsheets and have
	cataloged classes of problematic
	formulae~\cite{hermans2012detecting}~\cite{cunha2012towards}~\cite{asavametha2012detecting}, often accompanying them with detection tools~\cite{abreu2014smelling} and investigations into real datasets~\cite{jansen2015code}. For example, Hermans, leveraging her work with the aforementioned dataflow diagrams, has worked with assessing common inter-worksheet smells, such as feature envy and inappropriate intimacy, wherein references between worksheets (rather than cells) in a file suggest a problem~\cite{hermans2012detectinginter}. Other tools, like Badame's Excel refactoring~\cite{badame2012refactoring}, are concerned more with understanding the formula in service of changing them. Though \toolname supports the search for bad design, as we will see, the tool itself takes a much more agnostic approach in presentation, offering examples without regard for design quality. \par

	Implicit in this study is an exploration of the Excel API and how people use
	it. Previous research, such as the first study on the Enron
	spreadsheets~\cite{hermans2015enron} or in its comparison with the EUSUS
	corpus~\cite{jansen2015enron}, quantifies how often users employ certain
	functions but not how they combine them. Researchers have applied such
	questions to other contexts as well, such as Murphy and colleague's study into
	how Java developers use Eclipse and what commands they use most
	often~\cite{murphy2006java}. Others focus on the documentation of the API
	itself: Robillard and DeLine, for example conducted a series of surveys and
	interviews to diagnose common problems with learning APIs. They found that
	code examples, which is one of the focuses of this tool, is one of the most important
	aids to have in learning a new system~\cite{robillard2011field}. Though this
	paper applies the tool to the Enron corpus specifically, the tool itself is not
	limited to this; it can be readily applied to any collection of Excel
	spreadsheets a user gives it.
